APPM report - Draft

### 2022-11-11 paper_version/main.tex
fix some syntax errors in English

An asymptotic preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension. We extend their scheme to three dimensions. The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping. The scheme is designed to be AP as $\lambda_D \rightarrow 0$ and this is validated through numerical experiments. Special care is necessary for the boundary conditions which must be valid in both regimes. Additionally, if the electromagnetic fields have to be modelled in an insulating region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.

@@

\section{Full Discretization}
\subsection{Motivation: Reduction to 1D Discretization}
Our work is an extension of the 1D scheme proposed in \cite{degond_2012} towards a scheme in three dimensions. Therefore, it is compatible with the original 1D scheme when one considers its reduction to one dimension. This mental experiment aims to help readers understand how the new 3D scheme originates from the 1D one. 
\subsubsection{Projection to One Dimension} \label{sec:projection_to_1d}
Consider a mesh pair $(\mathcal{M}, \mathcal{M}')$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions on $x$-$y$ plane. On assuming the transverse invariance and rotational symmetry, one can reduce the 3D problem to a 1D one along $z$-axis. All the D.o.F. are now defined at the locations that are the projections of their original locations. For instance, an edge that is orthogonal to $z$-axis projects to a vertex while an edge parallel to $z$-axis projects to an edge. The procedure is sketched in Fig. \ref{fig:1d_reduction}.

@@

In \cite{degond_2012}, the authors consider a 1D Maxwell-Euler system by assuming vanishing traverse derivatives. Besides, $u_y, E_y, B_x, B_z$ are set zero for simplicity, which amounts to considering the TE mode. The 1D reduced Maxwell-Euler system and its quasi-neutral limit are

\vspace{-0.3cm}
\begin{minipage}{0.6\textwidth}
    \begin{align*}
        \partial_t n + \partial_z(nu_z) &= 0, \\
        \varepsilon^2[\partial_t(nu_x) + \partial_z(nu_zu_x)] &= - n(E_x - u_zB_y), \\
        \varepsilon^2[\partial_t(nu_z) + \partial_z(nu_z^2)] + \partial_z(p(n)) &= -n(E_z + u_xB_y), \\
        \partial_t B_y + \partial_z E_x &= 0, \\
        \lambda^2 \partial_t E_x + \partial_z B_y &= nu_x, \\
        \lambda^2 \partial_t E_z &= nu_z, \\
        \lambda^2 \partial_z E_z &= 1 - n,
    \end{align*}
\end{minipage}
$\xrightarrow[]{\lambda \rightarrow 0}$
\begin{minipage}{0.3\textwidth}
    \begin{align*}
        n &= 1,\\
        \varepsilon^2 \partial_t(u_x) &= - E_x, \\
        E_z + u_xB_y &= 0, \\
        u_z &= 0, \\
        \partial_t B_y + \partial_z E_x &= 0, \\
        \partial_z B_y &= nu_x,
    \end{align*}
\end{minipage}
where the subscript indicates the direction of the component. Here they consider a isentropic process with the equation of state $p(n) = n^\gamma$.

\subsubsection{1D Fully-discrete Plasma Model} \label{sec:1d_fully_discrete_model}
The following fully-discrete scheme is proposed in \cite{degond_2012}. The spatial discretization can be interpreted by the 1D projection procedure illustrated above. Here we want to discuss the time discretization with a focus on its semi-implicitness. From now on, we attach to variables a superscript involving $m$ to indicate the time step. The scheme is built on a uniform 1D mesh with cell size $h$ and evolves the system with time step $\delta^m := t^{m+1} - t^m$:  
\begin{align*}
    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\mycolorbox{orange!30}{f^{n,m+1/2}_{k+1/2} - f^{n,m+1/2}_{k-1/2}}}{h} &= 0, \\
    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{u_x,m}_{k+1/2} - f^{u_x,m}_{k-1/2}}{h} &= -\frac{n^m_k \mycolorbox{orange!30}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2},\\
    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{u_z,m}_{k+1/2} - f^{u_z,m}_{k-1/2}}{h} &= - \frac{n^m_k \mycolorbox{orange!30}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \\ 
    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\mycolorbox{orange!30}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \\
    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\mycolorbox{orange!30}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \mycolorbox{orange!30}{(nu_x)^{m+1}_k}, \\
    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \mycolorbox{orange!30}{f^{m+1}_{n,k+1/2}}, 
\end{align*}
where 
\begin{equation*}
    \Tilde{E}^m_{z,k} = \frac{1}{2}(E^m_{z,k+1/2} + E^m_{z,k-1/2}), \ \ \ \Tilde{B}^m_{y,k} = \frac{1}{2}(B^m_{y,k+1/2} + B^m_{y,k-1/2}),
\end{equation*}
are the averaged electromagnetic fields, and the fluxes read
\begin{align*}
    f^{n,m+1/2}_{k+1/2} & = \frac{1}{2}[\mycolorbox{orange!30}{(nu_z)^{m+1}_k + (nu_z)^{m+1}_{k+1}} + \mu^m_{k+1/2}(n^m_k - n^m_{k+1})], \\
    f^{u_x,m}_{k+1/2} & = \frac{1}{2}[(nu_zu_x)^{m}_k + (nu_zu_x)^{m}_{k+1} + \mu^m_{k+1/2}((nu_x)^m_k - (nu_x)^m_{k+1})], \\
    f^{u_z,m}_{k+1/2} & = \frac{1}{2}[(nu_z^2 + p(n)/\varepsilon^2)^{m}_k + (nu_z^2 + p(n)/\varepsilon^2)^{m}_{k+1} + \mu^m_{k+1/2}((nu_z)^m_k - (nu_z)^m_{k+1})].
\end{align*}
The implicit terms are highlighted. The implicitness of the electric field in the Lorentz force is shown to be necessary in \cite{fabre_1992} for the Euler-Poisson system. In \cite{degond_2012}, based on the linearized stability analysis, the author shows that the full-implicit treatment of the Maxwell equations is essential to the stability in the quasi-neutral limit. Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law have the same level of implicitness in order to guarantee the consistency with Gauss's law.

@@

The quantities with superscript $m+1/2$ implies its dependency on the quantities at both $m$-th and $(m+1)$-th iterations. In the Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal component velocity with respect to the dual face $\Tilde{A}_j$. We refrain the illustration of the collision term (\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case for the sake of simplicity.

@@

\subsubsection{CFL Condition}
It has been shown in \cite{degond_2012} that the stability-induced constraint on the time-step size does not depend on the value of $\lambda$ thanks to the implicitness in the discrete Maxwell system. However, the Euler system is discretized by an explicit scheme and thus still subject to a CFL condition.

In our case we have an conservation law with source terms. Let us consider the model equation
\begin{equation*}
    \partial_tu + c\partial_xu = \beta u, 
\end{equation*}
where $c>0$ and $\beta<0$ are constant. By a first-order upwind scheme
\begin{equation*}
    \delta_t^{-1}(u^{m+1}_k - u^m_k) + c\delta_x^{-1}(u^m_k - u^m_{k-1}) = \beta u^m_k,
\end{equation*}
we can perform Neumann analysis and deduce the CFL condition
\begin{equation*}
    \delta_t \leq \left[\frac{c}{\delta_x} + \frac{\beta}{2}\right]^{-1}.
\end{equation*}
On noticing the source term $\varepsilon_*^{-2}q_*(n\mathbf{u})^m_*\times\mathbf{B}^m$ in the momentum equation, we heuristically take the following restriction
\begin{equation*}
    \delta_t^m \leq \min_*\bigg\{\left[\frac{s^m_*}{\delta_x} + \frac{\varepsilon^{-2}_*|q_*||\mathbf{B}^m|}{2}\right]^{-1}\bigg\},
\end{equation*}
which is proven necessary by numerical experiments.

@@

The discrete Maxwell system (\ref{equ:maxwell_faraday_ap})-(\ref{equ:gauss_nonconducting_ap}) is closed provided (\ref{equ:discrete_ohm}) and can be evolved by solving a linear system. The Euler system (\ref{equ:euler_ap}) can afterwards be evolved explicitly.

\begin{remark}
    The formula (\ref{equ:discrete_ohm}) functions as Ohm's law in the discrete level and $\mathbb{M}_\sigma^m$ can be treated as a "conductivity" matrix. Since in the quasi-neutral limit $\lambda \rightarrow 0$ we lose control of the $\mathbf{E}$-field through its time derivative, $\mathbb{M}_\sigma^m$ is crucial to the stability of the scheme. Due to the fact that $\mathbf{j}$ and $\mathbf{d}$ are both defined on dual faces, it is reasonable to adopt a local relation between them. Therefore, we perform the \emph{diagonal lumping} trick on (\ref{equ:discrete_ohm}), i.e. rendering it diagonal by accumulating the row sum. We observe enhanced stability in the numerical experiments with very minor changes in the results.
\end{remark}
\section{Numerical Experiment}

We conduct numerical experiments based on the geometric setting and boundary conditions as presented in Section \ref{sec:BC}. The primal-dual mesh pair $(\mathcal{M}, \mathcal{M}')$ is generated based on the code developed in \cite[][ch. 1]{fuchs_2021}. An instance is shown in Fig. \ref{fig:primal_dual_meshes}. We consider a two-fluid plasma model which is composed of electrons and ions. We set the mass ratio $\varepsilon_e := m_e / m_i = 10^4$ and the collision parameter $\alpha^\text{coll} = 32$.
\begin{figure}
    \centering
    \includegraphics[scale=0.3]{primal_mesh.png}
    \hspace{1cm}
    \includegraphics[scale=0.3]{dual_mesh.png}
    \caption{Primal mesh (left) and dual mesh (right).}
    \label{fig:primal_dual_meshes}
\end{figure}
\subsection{Case 1: Quasi-1D Problem}
On noticing the radial symmetry of the domain as well as boundary conditions, we can simplify the governing equations defined at the axis of symmetry, i.e. $z$-axis in this case, thanks to vanishing radial components of the vector fields and their radial derivatives. The Euler-Maxwell system at the axis of symmetry reduces to
\begin{align*}
    &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z p_* = \varepsilon_*^{-2}q_*n_*E_z, \\
    &\partial_t (n_*e_*) + \partial_z (n_* h_* u_{*,z}) = \varepsilon_*^{-2} q_* n_* u_{*,z} E_z, \\
    \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
\end{align*}
which is similar to the 1D model in Section \ref{sec:projection_to_1d}. Therefore, it is reasonable to compare the results produced by the 1D scheme in Section \ref{sec:1d_fully_discrete_model} and the one on $z$-axis produced by the 3D scheme proposed in Section \ref{sec:3d_ap_scheme}. Fig. \ref{fig:z_axis_reduction} demonstrates good matching. 
\begin{figure}
    \centering
    \includegraphics{z_axis_reduction.eps}
    \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model. The results are both generated on meshes with 64 cells along $z$-axis. No friction term exists. $t = 5 \times 10^{-4}.$}
    \label{fig:z_axis_reduction}
\end{figure}

@@

We stick to the setting in Section \ref{sec:BC} and use the following initial conditions
\begin{equation*}
    n_\ast(\mathbf{x}, 0) = 1, \ \ \  p_\ast(\mathbf{x},0) = 1, \ \ \forall \mathbf{x}\in\Omega, \ast \in \{\text{electron}, \text{ion}\}.
\end{equation*}
All the other quantities are set zero initially. We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 1$, that is, a constant voltage is applied at the anode and want to see how the system is driven.

The cylindrical domain is 5.0 in length and 1.5 in radius. The plasma domain $\Omega_P$ has 1.0 in radius, i.e. the non-conducting domain $\Omega_N$ has an inner radius 1.0 and an outer radius 1.5.

@@

In Fig. \ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$ and $0$ are shown and the 3D structure of the electromagnetic field is visualized. A qualitative verification can be done in many aspects. First, the rotational symmetry of the problem is preserved. Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a relatively uniform value of approximately 0.2 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the curl-free property of the $\mathbf{E}$-field in steady state according to Faraday's law. This is also confirmed in Fig. \ref{fig:zaxis-data_vs_z-T_10}. Note that it does not hold for $\lambda = 1$ since the system has a large characteristic time and takes a long time to reach a equilibrium, which will be shown later in Fig. \ref{fig:origin-data_vs_time}. Besides, the $\mathbf{B}$-field is spiral-shaped and orthogonal to the $\mathbf{E}$-field. Also, under the driven force by the $\mathbf{E}$-field, the electrons move towards the anode $\Gamma^+_C$ as expected.
\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.25]{E-field_lambda-1.png}
        \includegraphics[scale=0.25]{B-field_lambda-1.png}
        \includegraphics[scale=0.25]{electronVel_lambda-1.png}
        \caption{$\lambda = 1.0$}
    \end{subfigure}
     \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.25]{E-field_lambda-1e-1.png}
        \hspace{0.3cm}
        \includegraphics[scale=0.25]{B-field_lambda-1e-1.png}
        \includegraphics[scale=0.25]{electronVel_lambda-1e-1.png}
        \caption{$\lambda = 1.0$}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.25]{E-field_lambda-0.png}
        \hspace{0.3cm}
        \includegraphics[scale=0.25]{B-field_lambda-0.png}
        \includegraphics[scale=0.25]{electronVel_lambda-0.png}
        \caption{$\lambda = 1.0$}
    \end{subfigure}
    \caption{Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (16 cells along $z$-axis). } 
    \label{fig:3d_vec_field_E_B_ue}
\end{figure}

Next, we perform a grid study. The norms of the solutions under mesh refinement is shown in Fig. \ref{fig:grid_study_3d}. Due to the high computational cost in 3D simulations, a reference solutions produced by a highly-refined mesh is not accessible. That is why we compute the norms and display results only generated by relatively coarse meshes. Fig. \ref{fig:grid_study_3d} gives an indication that the solutions are stable under mesh refinement. To reveal more features of the solutions, in Fig. \ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot quantities at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$. Qualitatively the same solutions are produced under different meshes.

>>>>

An asymptotic-preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension. We extend their scheme to three dimensions. The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping. The scheme is designed to be AP as $\lambda_D \rightarrow 0$ and this is validated through numerical experiments. Special care is necessary for the boundary conditions which must be valid in both regimes. Additionally, if the electromagnetic fields have to be modelled in an insulating region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.

@@

\section{Full Discretization}
\subsection{Motivation: Reduction to 1D Discretization}
Our work is an extension of the 1D scheme proposed in \cite{degond_2012} towards a scheme in three dimensions. Therefore, it is compatible with the original 1D scheme when one considers its reduction to one dimension. This mental experiment aims to help readers understand how the new 3D scheme originates from the 1D one. 
\subsubsection{Projection to One Dimension} \label{sec:projection_to_1d}
Consider a mesh pair $(\mathcal{M}, \mathcal{M}')$ that are constructed by 2D extrusion along $z$-axis and are unbounded along transverse directions on $x$-$y$ plane. On assuming the transverse invariance and rotational symmetry, one can reduce the 3D problem to a 1D one along the $z$-axis. All the D.o.F. are now defined at the locations that are the projections of their original locations. For instance, an edge that is orthogonal to the $z$-axis projects to a vertex while a parallel edge to the $z$-axis is projected to an edge. The procedure is sketched in Fig. \ref{fig:1d_reduction}.

@@

In \cite{degond_2012}, the authors consider a 1D Maxwell-Euler system by assuming vanishing traverse derivatives. Besides, $u_y, E_y, B_x$, and $B_z$ are set to zero for simplicity, which amounts to considering the TE mode. The 1D reduced Maxwell-Euler system and its quasi-neutral limit are

\vspace{-0.3cm}
\begin{minipage}{0.6\textwidth}
    \begin{align*}
        \partial_t n + \partial_z(nu_z) &= 0, \\
        \varepsilon^2[\partial_t(nu_x) + \partial_z(nu_zu_x)] &= - n(E_x - u_zB_y), \\
        \varepsilon^2[\partial_t(nu_z) + \partial_z(nu_z^2)] + \partial_z(p(n)) &= -n(E_z + u_xB_y), \\
        \partial_t B_y + \partial_z E_x &= 0, \\
        \lambda^2 \partial_t E_x + \partial_z B_y &= nu_x, \\
        \lambda^2 \partial_t E_z &= nu_z, \\
        \lambda^2 \partial_z E_z &= 1 - n,
    \end{align*}
\end{minipage}
$\xrightarrow[]{\lambda \rightarrow 0}$
\begin{minipage}{0.3\textwidth}
    \begin{align*}
        n &= 1,\\
        \varepsilon^2 \partial_t(u_x) &= - E_x, \\
        E_z + u_xB_y &= 0, \\
        u_z &= 0, \\
        \partial_t B_y + \partial_z E_x &= 0, \\
        \partial_z B_y &= nu_x,
    \end{align*}
\end{minipage}
where the subscript indicates the direction of the component. Here they consider an isentropic process with the equation of state $p(n) = n^\gamma$.

\subsubsection{1D Fully-discrete Plasma Model} \label{sec:1d_fully_discrete_model}
The following fully-discrete scheme is proposed in \cite{degond_2012}. The spatial discretization can be interpreted by the 1D projection procedure illustrated above. Here we want to discuss time discretization with a focus on its semi-implicitness. From now on, we attach to variables a superscript involving $m$ to indicate the time step. The scheme is built on a uniform 1D mesh with cell size $h$ and evolves the system with time step $\delta^m := t^{m+1} - t^m$:  
\begin{align*}
    \frac{n^{m+1}_k - n^m_k}{\delta^m} + \frac{\mycolorbox{orange!30}{f^{n,m+1/2}_{k+1/2} - f^{n,m+1/2}_{k-1/2}}}{h} &= 0, \\
    \frac{(nu_x)^{m+1}_k - (nu_x)^m_k}{\delta^m} + \frac{f^{u_x,m}_{k+1/2} - f^{u_x,m}_{k-1/2}}{h} &= -\frac{n^m_k \mycolorbox{orange!30}{E^{m+1}_{x,k}}}{\varepsilon^2} + \frac{n^m_k u^m_{z,k}\Tilde{B}^m_{y,k}}{\varepsilon^2},\\
    \frac{(nu_z)^{m+1}_k - (nu_z)^m_k}{\delta^m} + \frac{f^{u_z,m}_{k+1/2} - f^{u_z,m}_{k-1/2}}{h} &= - \frac{n^m_k \mycolorbox{orange!30}{\Tilde{E}^{m+1}_{z,k}}}{\varepsilon^2} - \frac{n^m_k u^m_{x,k}\Tilde{B}^m_{y,k}}{\varepsilon^2}, \\ 
    \frac{B^{m+1}_{y,k+1/2} - B^{m}_{y,k+1/2}}{\delta^m} + \frac{\mycolorbox{orange!30}{E^{m+1}_{x,k+1} - E^{m+1}_{x,k}}}{h} &= 0, \\
    \lambda^2 \frac{E^{m+1}_{x,k} - E^{m}_{x,k}}{\delta^m} + \frac{\mycolorbox{orange!30}{B^{m+1}_{y,k+1/2} - B^{m+1}_{y,k-1/2}}}{h} &= \mycolorbox{orange!30}{(nu_x)^{m+1}_k}, \\
    \lambda^2 \frac{E^{m+1}_{z,k+1/2} - E^{m}_{z,k+1/2}}{\delta^m} &= \mycolorbox{orange!30}{f^{m+1}_{n,k+1/2}}, 
\end{align*}
where 
\begin{equation*}
    \Tilde{E}^m_{z,k} = \frac{1}{2}(E^m_{z,k+1/2} + E^m_{z,k-1/2}), \ \ \ \Tilde{B}^m_{y,k} = \frac{1}{2}(B^m_{y,k+1/2} + B^m_{y,k-1/2}),
\end{equation*}
are the averaged electromagnetic fields, and the fluxes read
\begin{align*}
    f^{n,m+1/2}_{k+1/2} & = \frac{1}{2}[\mycolorbox{orange!30}{(nu_z)^{m+1}_k + (nu_z)^{m+1}_{k+1}} + \mu^m_{k+1/2}(n^m_k - n^m_{k+1})], \\
    f^{u_x,m}_{k+1/2} & = \frac{1}{2}[(nu_zu_x)^{m}_k + (nu_zu_x)^{m}_{k+1} + \mu^m_{k+1/2}((nu_x)^m_k - (nu_x)^m_{k+1})], \\
    f^{u_z,m}_{k+1/2} & = \frac{1}{2}[(nu_z^2 + p(n)/\varepsilon^2)^{m}_k + (nu_z^2 + p(n)/\varepsilon^2)^{m}_{k+1} + \mu^m_{k+1/2}((nu_z)^m_k - (nu_z)^m_{k+1})].
\end{align*}
The implicit terms are highlighted. The implicitness of the electric field in the Lorentz force is shown to be necessary in \cite{fabre_1992} for the Euler-Poisson system. In \cite{degond_2012}, based on the linearized stability analysis, the author shows that the full-implicit treatment of the Maxwell equations is essential to the stability in the quasi-neutral limit. Besides, the mass flux in the mass conservation equation and the current in Amp\`{e}re's law has the same level of implicitness to guarantee consistency with Gauss's law.

@@

The quantities with superscript $m+1/2$ indicate their dependency on the quantities at both $m$-th and $(m+1)$-th iterations. In the Rusanov flux (\ref{equ:flux_ap}), we denote by $u_\perp$ the normal component velocity with respect to the dual face $\Tilde{A}_j$. We restrain the illustration of the collision term (\ref{equ:R_coll_ap}) (\ref{equ:Q_coll_ap}) to the two-species case for the sake of simplicity.

@@

\subsubsection{CFL Condition}
It has been shown in \cite{degond_2012} that the stability-induced constraint on the time-step size does not depend on the value of $\lambda$ thanks to the implicitness in the discrete Maxwell system. However, the Euler system is discretized by an explicit scheme and thus is still subject to a CFL condition.

In our case, we have a conservation law with source terms. Let us consider the model equation
\begin{equation*}
    \partial_tu + c\partial_xu = \beta u, 
\end{equation*}
where $c>0$ and $\beta<0$ are constant. By a first-order upwind scheme
\begin{equation*}
    \delta_t^{-1}(u^{m+1}_k - u^m_k) + c\delta_x^{-1}(u^m_k - u^m_{k-1}) = \beta u^m_k,
\end{equation*}
we can perform Neumann analysis and deduce the CFL condition
\begin{equation*}
    \delta_t \leq \left[\frac{c}{\delta_x} + \frac{\beta}{2}\right]^{-1}.
\end{equation*}
On noticing the source term $\varepsilon_*^{-2}q_*(n\mathbf{u})^m_*\times\mathbf{B}^m$ in the momentum equation, we heuristically take the following restriction
\begin{equation*}
    \delta_t^m \leq \min_*\bigg\{\left[\frac{s^m_*}{\delta_x} + \frac{\varepsilon^{-2}_*|q_*||\mathbf{B}^m|}{2}\right]^{-1}\bigg\},
\end{equation*}
which is proven necessary by numerical experiments.

@@

The discrete Maxwell system (\ref{equ:maxwell_faraday_ap})-(\ref{equ:gauss_nonconducting_ap}) is closed provided (\ref{equ:discrete_ohm}) and can be evolved by solving a linear system. The Euler system (\ref{equ:euler_ap}) can afterward be evolved explicitly.

\begin{remark}
    The formula (\ref{equ:discrete_ohm}) functions as Ohm's law in the discrete level and $\mathbb{M}_\sigma^m$ can be treated as a "conductivity" matrix. Since in the quasi-neutral limit $\lambda \rightarrow 0$ we lose control of the $\mathbf{E}$-field through its time derivative, $\mathbb{M}_\sigma^m$ is crucial to the stability of the scheme. Since $\mathbf{j}$ and $\mathbf{d}$ are both defined on dual faces, it is reasonable to adopt a local relation between them. Therefore, we perform the \emph{diagonal lumping} trick on (\ref{equ:discrete_ohm}), i.e. rendering it diagonal by accumulating the row sum. We observe enhanced stability in the numerical experiments with very minor changes in the results.
\end{remark}
\section{Numerical Experiment}

We conduct numerical experiments based on the geometric setting and boundary conditions as presented in Section \ref{sec:BC}. The primal-dual mesh pair $(\mathcal{M}, \mathcal{M}')$ is generated based on the code developed in \cite[][ch. 1]{fuchs_2021}. An instance is shown in Fig. \ref{fig:primal_dual_meshes}. We consider a two-fluid plasma model which is composed of electrons and ions. We set the mass ratio $\varepsilon_e := m_e / m_i = 10^4$ and the collision parameter $\alpha^\text{coll} = 32$.
\begin{figure}
    \centering
    \includegraphics[scale=0.3]{primal_mesh.png}
    \hspace{1cm}
    \includegraphics[scale=0.3]{dual_mesh.png}
    \caption{Primal mesh (left) and dual mesh (right).}
    \label{fig:primal_dual_meshes}
\end{figure}
\subsection{Case 1: Quasi-1D Problem}
On noticing the radial symmetry of the domain as well as boundary conditions, we can simplify the governing equations defined at the axis of symmetry, i.e. $z$-axis in this case, thanks to vanishing radial components of the vector fields and their radial derivatives. The Euler-Maxwell system at the axis of symmetry reduces to
\begin{align*}
    &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z p_* = \varepsilon_*^{-2}q_*n_*E_z, \\
    &\partial_t (n_*e_*) + \partial_z (n_* h_* u_{*,z}) = \varepsilon_*^{-2} q_* n_* u_{*,z} E_z, \\
    \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
\end{align*}
which is similar to the 1D model in Section \ref{sec:projection_to_1d}. Therefore, it is reasonable to compare the results produced by the 1D scheme in Section \ref{sec:1d_fully_discrete_model} and the one on $z$-axis produced by the 3D scheme proposed in Section \ref{sec:3d_ap_scheme}. Fig. \ref{fig:z_axis_reduction} demonstrates good matching. 
\begin{figure}
    \centering
    \includegraphics{z_axis_reduction.eps}
    \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model. The results are both generated on meshes with 64 cells along the $z$-axis. No friction term exists. $t = 5 \times 10^{-4}.$}
    \label{fig:z_axis_reduction}
\end{figure}

@@

We stick to the setting in Section \ref{sec:BC} and use the following initial conditions
\begin{equation*}
    n_\ast(\mathbf{x}, 0) = 1, \ \ \  p_\ast(\mathbf{x},0) = 1, \ \ \forall \mathbf{x}\in\Omega, \ast \in \{\text{electron}, \text{ion}\}.
\end{equation*}
All the other quantities are set to zero initially. We set $\varphi(\mathbf{x}, t)|_{\Gamma_C^-} = 0, \varphi(\mathbf{x}, t)|_{\Gamma_C^+} = 1$, that is, a constant voltage is applied at the anode and want to see how the system is driven.

The cylindrical domain is 5.0 in length and 1.5 in radius. The plasma domain $\Omega_P$ has 1.0 in radius, i.e. the non-conducting domain $\Omega_N$ has an inner radius of 1.0 and an outer radius of 1.5.

@@

In Fig. \ref{fig:3d_vec_field_E_B_ue}, the numerical solutions for $\lambda = 1.0, 0.1$ and $0$ are shown and the 3D structure of the electromagnetic field is visualized. Qualitative verification can be done in many aspects. First, the rotational symmetry of the problem is preserved. Second, the $\mathbf{E}$-field points from $\Gamma^+_C$ to $\Gamma^-_C$ with a relatively uniform value of approximately 0.2 ($=\text{applied voltage}/\text{cylinder length}$) as a consequence of the curl-free property of the $\mathbf{E}$-field in the steady state according to Faraday's law. This is also confirmed in Fig. \ref{fig:zaxis-data_vs_z-T_10}. Note that it does not hold for $\lambda = 1$ since the system has a large characteristic time and takes a long time to reach an equilibrium, which will be shown later in Fig. \ref{fig:origin-data_vs_time}. Besides, the $\mathbf{B}$-field is spiral-shaped and orthogonal to the $\mathbf{E}$-field. Also, under the driven force by the $\mathbf{E}$-field, the electrons move towards the anode $\Gamma^+_C$ as expected.
\begin{figure}
    \centering
    \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.25]{E-field_lambda-1.png}
        \includegraphics[scale=0.25]{B-field_lambda-1.png}
        \includegraphics[scale=0.25]{electronVel_lambda-1.png}
        \caption{$\lambda = 1.0$}
    \end{subfigure}
     \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.25]{E-field_lambda-1e-1.png}
        \hspace{0.3cm}
        \includegraphics[scale=0.25]{B-field_lambda-1e-1.png}
        \includegraphics[scale=0.25]{electronVel_lambda-1e-1.png}
        \caption{$\lambda = 1.0$}
    \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \draw[blue, -to] (0,0) -- (20:0.7) node[right]{\small $z$};
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
        \end{tikzpicture}
        \includegraphics[scale=0.25]{E-field_lambda-0.png}
        \hspace{0.3cm}
        \includegraphics[scale=0.25]{B-field_lambda-0.png}
        \includegraphics[scale=0.25]{electronVel_lambda-0.png}
        \caption{$\lambda = 1.0$}
    \end{subfigure}
    \caption{Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (16 cells along $z$-axis). } 
    \label{fig:3d_vec_field_E_B_ue}
\end{figure}

Next, we perform a grid study. The norms of the solutions under mesh refinement are shown in Fig. \ref{fig:grid_study_3d}. Due to the high computational cost in 3D simulations, reference solutions produced by a highly-refined mesh are not accessible. That is why we compute the norms and display results only generated by relatively coarse meshes. Fig. \ref{fig:grid_study_3d} indicates that the solutions are stable under mesh refinement. To reveal more features of the solutions, in Fig. \ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0}, we plot quantities at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$. Qualitatively the same solutions are produced under different meshes.
